---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
  /* Add CSS for the hover effect */
  img:hover {
    height: 150px; /* Change this value to the desired enlarged height */
    width: 150px; /* Change this value to the desired enlarged width */
  }
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
 
## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css
  

```{r, echo=FALSE, results='asis'}
library(DT)
dirinput <- 'C:/Users/GFraga/Desktop/AFFORD_THUMBS/Spring/'
       
fnames <- dir(dirinput)
metadata <- as.data.frame(fnames[grepl('^JP*.*.jpg$',fnames)])
colnames(metadata) <- 'file'
# split names 
parts <- strsplit(metadata$file,'-')
basenames <- sapply(strsplit(metadata$file,'.tif'),'[[',1)
metadata$specID <- sapply(strsplit(basenames,'-'),'[[',1)
metadata$status <- sapply(strsplit(basenames,'-'),'[[',2)
metadata$scan <- sapply(strsplit(basenames,'-'),'[[',3)
metadata$seq <- sapply(strsplit(basenames,'_'),'[[',2)
metadata$rec <- sapply(strsplit(basenames,'_rec'),'[[',2)


# add html component 

metadata$link <- metadata$file
metadata$link <- paste0('<img src=\'Spring/', metadata$link, '\' height=\'50\' witdth = \'50\'></img>')

# table
 datatable(
    metadata, filter = "top",
    rownames=FALSE, width="100%", 
    class='compact cell-border hover', extensions='Buttons',
    options=list(dom='Bfrtip',buttons=c('copy','csv','excel')),
    escape=FALSE
  )
 



#fileinput <- 'C:/Users/GFraga/Desktop/AFFORD_THUMBS/Metadata.xlsx' # Path will change to read file from github repo
#library(DT)
# here some validation checks should be included 
#data <- readxl::read_excel(fileinput)

#plot table
#library(reactable)

 

 



#reactable::reactable(data, filterable = TRUE, minRows = 10, searchable = TRUE, columns = list( 
 #                       Link = colDef(cell = function(value, index) {
  #                        # Render text of 'Link' column as a hyperlink
   #                       htmltools::tags$a(href = url, target = "_blank", as.character(value))
    #                    }))) 
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
